Human Pose Estimation for Video Game Control

### 2022-05-09 paper/paper.tex
Added another figure and fixed some typos

\begin{abstract}
    Current methods of interacting with computers are flawed in a 
    couple of key ways, especially when it comes to video games: they fail to map physically-intuitive motions to their computer 
    control counterparts, and they rely heavily on a user's fine-motor skills, 
    which are heavily impacted by factors such as muscle coordination disabilities 
    and old age. In this paper, we propose a system of computer control through 
    gesture tracking via real-time human pose estimation on an embedded device, 
    which is capable of addresssing these issues, by mapping general physically-intuitive 
    motions into computer control. Furthermore, our device boasts low latency in 
    the human-computer interaction, and is minimally intrustive to the computer being 
    controlled. We test the viability of our system as a computer-control device by playing two 
    video games using only gestures.
\end{abstract}

\section{Introduction}
The human-computer interfaces behind many modern video games use either handheld 
joystick controllers or keyboard and mouse input, which are examples
of typical human input device for computers, monitors, televisions, etc. There are two 
major drawbacks to traditional human input systems that are often overlooked: the input needed 
to achieve a certain effect has little to no correspondence to a physically-intuitive set 
of motions, and more importantly, inputs are heavily dependent on the user's fine motor skills. 
Fine motor skills used to interact with modern technology are heavily affected by factors such 
as muscular coordination disorders and old age. Computer vision, particularly the processes 
of human pose estimation and motion tracking may allow us to create human-computer interfaces 
that link computer control to physically-intuitive human motion inputs with little dependence on 
fine motor ability or additional physical input devices. We propose a vision-based computer-input 
system that maps gestures and motion of the user's body into computer input. We test the system's 
effectiveness with the playability of two simple video games as metrics. In order to demonstrate 
the versatility of our phased-approach to gesture-based control, we select a car-racing game and 
the Google Chrome Dino Racer game as test video games. Such a system, when expanded to replicating 
general keyboard + mouse control, would be instrumental in improving the accessibility of 
modern technology, with implementations far beyond the scope of computer games.

@@

>>>>

\begin{abstract}
    Current methods of interacting with computers are flawed in a 
    couple of key ways, especially when it comes to video games: they fail to map physically-intuitive motions to their computer 
    control counterparts, and they rely on a user's fine-motor skills, 
    which are heavily impacted by factors such as muscle coordination disabilities 
    and old age. In this paper, we propose a system of computer control through 
    gesture tracking via real-time human pose estimation on an embedded device, 
    which is capable of addresssing these issues, by mapping general physically-intuitive 
    motions into computer control. Furthermore, our device boasts low latency in 
    the human-computer interaction, and is minimally intrustive to the computer being 
    controlled. We test the viability of our system as a computer-control device by playing two 
    video games using only gestures.
\end{abstract}

\section{Introduction}
The human-computer interfaces behind many modern video games use either handheld 
joystick controllers or keyboard and mouse input, which are examples
of typical human input device for computers, monitors, televisions, etc. There are two 
major drawbacks to traditional human input systems that are often overlooked: the input needed 
to achieve a certain effect has little to no correspondence to a physically-intuitive set 
of motions, and more importantly, inputs are heavily dependent on the user's fine motor skills. 
Fine motor skills used to interact with modern technology are heavily affected by factors such 
as muscular coordination disorders and old age. Computer vision, particularly the processes 
of human pose estimation and motion tracking, may allow us to create human-computer interfaces 
that link computer control to physically-intuitive human motion inputs with little dependence on 
fine motor ability or additional physical input devices. We propose a vision-based computer-input 
system that maps gestures and motion of the user's body into computer input. We test the system's 
effectiveness with the playability of two simple video games as metrics. In order to demonstrate 
the versatility of our phased-approach to gesture-based control, we select a car-racing game and 
the Google Chrome Dino Racer game as test video games. Such a system, when expanded to replicating 
general keyboard + mouse control, would be instrumental in improving the accessibility of 
modern technology, with implementations far beyond the scope of computer games.

@@

\begin{figure}
    \centering
    \includegraphics[width = .6\linewidth]{images/jetson_nano.jpg}
    \caption{NVIDIA Jetson Nano, a single-board computer capable of 
    low-latency deep model inference.}
\end{figure}
